Multiple Kernelized Correlation Filters based High Speed Target Following

### 2017-04-09 draft.tex
Removed duplicate bib entry; cleaned up a bit.

The contributions of this study are as follows.
\begin{itemize}
\item We build a highly efficient ($\geq300$ fps) scale adaptive multiple kernelized correlation filter based tracker that outperforms the original KCF implementation with fixed scale framework both in terms of accuracy and performance. The studies following the KCF improved the fixed scale framework by running detection on a number of candidate ROIs to figure out the new scale of the object after estimating the translation of the object. This approach adds additional complexity to the original KCF implementation and drags down the run-time performance from $300$ fps to less than $100$ fps.
\item We integrate the Particle Filter into the Multiple KCFs tracking as an additional filter that can avoid the drift due to one of the correlation filters we employ in our framework.
\item We propose a target re-detection module that can minimize the target loss due to the scale filter that learns the object model using only-object area. Also, the target re-detection step is required to handle severe occlusions, pose variations, illumination changes and fast motion.
\item Since our visual tracker mostly focuses on tracking objects from aerial moving platforms, we design a new robust target-to-camera distance estimation method. This way, a safe distance between the target and the camera-platform can be preserved.
\end{itemize}

@@

The Kernelized Correlation Filter tracker has recently been increasingly popular due to its operation at hundreds of frames per second with state-of-the-art tracking capabilities in
challenging cases. Its computational efficiency arises from its use of the discrete fourier transform of the circulant matrix and frequency domain element-wise operations knows hadamard product and division. The first example of frequency domain trackers is the Linear Correlation Filter tracker known as MOSSE tracker. It minimizes the ridge regression function
in the frequency domain using a single template with continous desired gaussian response. The KCF tracker, on the other hand, minimizes the regularized ridge regression function shown below. 

@@

where $y$ represents the desired continous response whereas $h$ and $x_{c}$ represents the learned correlation filter and training template for the given channel. The $c$ parameter included in \cite{henriques2015high,galoogahi2013multi} makes it possible to integrate multi-channel features such as HoG and colour into the ridge regression function. The closed-form solution for the eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the derivative of $E$ w.r.t $w$ to $0$. The solution in the primal domain can be formulated as

@@

where $X$ and $\lambda$ represent the training samples and regularization term. The same cost function in the Fourier domain can be represented as

@@

More information on the spatial and fourier domain solutions can be found in \cite{henriques2015high}. The MOSSE tracker does not make use of $\lambda$ and only one training sample with desired response is used to update $w$. This framework does not include enough background information into the training framework with a single template. The application of the circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many background patches at a similar computational complexity. A circulant matrix $C$ includes the circularly shifted patches of the positive training sample $x$ by the cylic shift operator $P$. By applying shifting operation to the base sample, we can generate the circulant matrix as

@@

The circulant matrix of a base sample $x$ can be interpreted as the rows of a training matrix $X$ where each row represents features of a training sample. Mathematically, this can be written as

@@

In this form, eq.~\ref{eq:SpatialSolution} and~\ref{eq:FourierSolution} could prohibit us from implementing a high speed object tracking as we need to perform large number of element-wise division and multiplication operations. However, we know from \cite{gray2006toeplitz} that all circulant matrices are represented diagonally by the Fourier Transform regardless of the base sample $x$ as shown below.

@@

where $F$ denotes a constant Fourier Transform matrix and $x$ is the Discrete Fourier Transform of the base sample $x$. To simplify the cost function formulation in eq.~\ref{eq:FourierSolution} we multiply $X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding 

@@

Finally, the eq.~\ref{eq:SimplificationX} can used to formulate the solution vector in Fourier domain $\hat{w}$ as

@@

For detailed documentation of the circulant matrix theorem based frequency domain solution can be found in \cite{henriques2012exploiting,henriques2015high}.

@@

\section{Multiple Kernelized Correlation Filter Based Tracking}
\label{sc:MKCF}
The KCF with Multi-channel features outperforms the other state-of-the-art object traking algorithms both in terms of run-time performance and tracking accuracy. However, it lack scale adaptation module or the naive scale adaptation method added into the KCF reduces the frames per second from $\geq300$ fps to less than $100$ fps. One straightforward method is to run detection on ROIs with different sizes determined by pre-defined scale ratios \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All these method increases the computational complexity of tracking by running detection on a number of ROIs. Another scale update method in Correlation Filter framework was proposed by \cite{zhang2014fast}. It uses the MOSSE tracker to estimate translation of an object. The scale is updated in a naive way where the confidence map is used to determine the scale change between successive frames. For instance, their method assumes similar scale in between two consecutive frames given similar confidences. With this simple method, we do not need to run detection on different ROIs at a given frame and perform tracking at $\geq300$ fps. In this study, we propose the use of Multiple KCFs in an intuitive way to perform robust scale-adaptive tracking at more than $300$ fps. Our approach is inspired by \cite{ma2015long} where two KCFs are employed as translation and scale filters. It first estimates translation using the translation filter learned on \textit{target}$+$\textit{background} area. Then, the scale filter learned on the \textit{target} area is used to estimate new scale of the target at the estimated position. Application of translation and scale filter at each frame reduces run-time performance ($\leq50 fps$) as we need to run detection and training on both filters. Similarly, we learn three different correlation filters specializing on different aspects of tracking and addresses the weakness of each other, resulting in more robust tracking. We name these filters as \textit{target}+\textit{small background} translation filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and \textit{target}+\textit{large background} translation filter ($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at each frame, we can achieve the targeted operation frame rate. The fig.~\ref{fig:Filters} shows the size of the ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning windows assigned and desired Gaussian responses assigned to each one.

>>>>

The contributions of this study are as follows.
\begin{itemize}

\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

\item We integrate the Particle Filter into the Multiple KCFs tracking
  as an additional filter that can avoid the drift due to one of the
  correlation filters we employ in our framework.

\item We propose a target re-detection module that can minimize the
  target loss due to the scale filter that learns the object model
  using only-object area. Also, the target re-detection step is
  required to handle severe occlusions, pose variations, illumination
  changes and fast motion.

\item Since our visual tracker mostly focuses on tracking objects from
  aerial moving platforms, we design a new robust target-to-camera
  distance estimation method. This way, a safe distance between the
  target and the camera-platform can be preserved.

\end{itemize}

@@

The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities in challenging
cases. Its computational efficiency arises from its use of the
discrete fourier transform of the circulant matrix and frequency
domain element-wise operations knows hadamard product and
division. The first example of frequency domain trackers is the Linear
Correlation Filter tracker known as MOSSE tracker. It minimizes the
ridge regression function in the frequency domain using a single
template with continous desired gaussian response. The KCF tracker, on
the other hand, minimizes the regularized ridge regression function
shown below.

@@

where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. The solution in the primal domain
can be formulated as

@@

where $X$ and $\lambda$ represent the training samples and
regularization term. The same cost function in the Fourier domain can
be represented as

@@

More information on the spatial and fourier domain solutions can be
found in \cite{henriques2015high}. The MOSSE tracker does not make use
of $\lambda$ and only one training sample with desired response is
used to update $w$. This framework does not include enough background
information into the training framework with a single template. The
application of the circulant matrix theorem into the
eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many
background patches at a similar computational complexity. A circulant
matrix $C$ includes the circularly shifted patches of the positive
training sample $x$ by the cylic shift operator $P$. By applying
shifting operation to the base sample, we can generate the circulant
matrix as

@@

The circulant matrix of a base sample $x$ can be interpreted as the
rows of a training matrix $X$ where each row represents features of a
training sample. Mathematically, this can be written as

@@

In this form, eq.~\ref{eq:SpatialSolution}
and~\ref{eq:FourierSolution} could prohibit us from implementing a
high speed object tracking as we need to perform large number of
element-wise division and multiplication operations. However, we know
from \cite{gray2006toeplitz} that all circulant matrices are
represented diagonally by the Fourier Transform regardless of the base
sample $x$ as shown below.

@@

where $F$ denotes a constant Fourier Transform matrix and $x$ is the
Discrete Fourier Transform of the base sample $x$. To simplify the
cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding

@@

Finally, the eq.~\ref{eq:SimplificationX} can used to formulate the
solution vector in Fourier domain $\hat{w}$ as

@@

For detailed documentation of the circulant matrix theorem based
frequency domain solution can be found in
\cite{henriques2012exploiting,henriques2015high}.

@@

%-------------------------------------------------------------------
\section{Multiple Kernelized Correlation Filter Based Tracking}
\label{sc:MKCF}
%------------------------------------------------------------------
The KCF with Multi-channel features outperforms the other
state-of-the-art object traking algorithms both in terms of run-time
performance and tracking accuracy. However, it lack scale adaptation
module or the naive scale adaptation method added into the KCF reduces
the frames per second from $\geq300$ fps to less than $100$ fps. One
straightforward method is to run detection on ROIs with different
sizes determined by pre-defined scale ratios
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All
these method increases the computational complexity of tracking by
running detection on a number of ROIs. Another scale update method in
Correlation Filter framework was proposed by \cite{zhang2014fast}. It
uses the MOSSE tracker to estimate translation of an object. The scale
is updated in a naive way where the confidence map is used to
determine the scale change between successive frames. For instance,
their method assumes similar scale in between two consecutive frames
given similar confidences. With this simple method, we do not need to
run detection on different ROIs at a given frame and perform tracking
at $\geq300$ fps. In this study, we propose the use of Multiple KCFs
in an intuitive way to perform robust scale-adaptive tracking at more
than $300$ fps. Our approach is inspired by \cite{ma2015long} where
two KCFs are employed as translation and scale filters. It first
estimates translation using the translation filter learned on
\textit{target}$+$\textit{background} area. Then, the scale filter
learned on the \textit{target} area is used to estimate new scale of
the target at the estimated position. Application of translation and
scale filter at each frame reduces run-time performance ($\leq50 fps$)
as we need to run detection and training on both filters. Similarly,
we learn three different correlation filters specializing on different
aspects of tracking and addresses the weakness of each other,
resulting in more robust tracking. We name these filters as
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
each frame, we can achieve the targeted operation frame rate. The
fig.~\ref{fig:Filters} shows the size of the ROIs associated with
$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
windows assigned and desired Gaussian responses assigned to each one.
